Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-07-02 latex/CEUR/paper.tex
Combined Misclassification AUROC and AUPR tables into one to save space. Removed table of classes to save space.

\begin{table}
% \renewcommand{\arraystretch}{1.5}
\caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
\label{tab::classes}
\centering
\begin{tabular}{NNcZ}
\hline
\bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
\hline
$0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
$1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
$2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
$3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
$4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
$5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
$6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
$7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
$8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
$9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
$10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
$11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
$12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
$13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
$14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
$15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
$16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
$17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
$18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
$19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
$20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
\hline
\end{tabular}
\end{table}

@@

The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc} and Table \ref{tab::misc_aupr} respectively.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
GCN & - & - &-&-&$0.887$ \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
\label{tab::misc_aupr}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
GCN & - & -  &-&-&$0.606$ \\ 
Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets. There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or by assessing a variety of entirely different function.
%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to ...
\end{acknowledgments}

>>>>

% \begin{table}
% % \renewcommand{\arraystretch}{1.5}
% \caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
% \label{tab::classes}
% \centering
% \begin{tabular}{NNcZ}
% \hline
% \bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
% \hline
% $0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
% $1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
% $2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
% $3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
% $4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
% $5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
% $6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
% $7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
% $8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
% $9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
% $10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
% $11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
% $12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
% $13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
% $14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
% $15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
% $16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
% $17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
% $18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
% $19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
% $20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
% \hline
% \end{tabular}
% \end{table}

@@

The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc}.

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Y|ccccc|ccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
                        & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&0.352&0.398&0.467&0.237&0.474    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&0.659&0.545&0.649&0.206&0.672  \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&0.451&0.484&0.591&0.278&0.579  \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&0.489&0.558&0.633&0.268&0.616  \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&0.472&0.538&-&-&0.595  \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$&0.417&0.566&-&-&0.606  \\
GCN & - & - &-&-&$0.887$&-&-&-&-&0.606  \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&0.619&0.243&0.600  \\ \hline
\end{tabular}
\end{center}
\end{table*}

% \begin{table*}[!t]
% \renewcommand{\arraystretch}{1.3}
% \caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
% \label{tab::misc_aupr}
% \small
% \begin{center}
% \begin{tabular}{cccccc}
% \hline
% \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
%       & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
% S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
% S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
% S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
% S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
% S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
% S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
% GCN & - & -  &-&-&$0.606$ \\ 
% Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
% \end{tabular}
% \end{center}
% \end{table*}

@@

Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets. There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or considering different prior computation methods entirely.
%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to ...
\end{acknowledgments}
